The Sub-Millimetre User Reduction Facility: an iterative map-maker for \scuba

### 2012-08-14 smurf_paper.tex
Add standard JCMT acknowledgment
Needs some clarification on the words for EC CANFAR funding.

\textit{Presumably the standard telescope acknowledgment here plus a
thank you to CFI for funding the DR work. Ed should probably thank
both CANFAR and JAC for additionally funding although his JAC funding
is noted in the affiliation.}

>>>>

The James Clerk Maxwell Telescope is operated by the Joint Astronomy
Centre on behalf of the Science and Technology Facilities Council of
the United Kingdom, the Netherlands Organisation for Scientific
Research, and the National Research Council of Canada. Additional
funds for the contruction of SCUBA-2 were provided by the Canada
Foundation for Innovation. EC thanks CANARIE/CANFAR for additional
funding.

\textit{Is there some kind of grant number that has to be referenced
  for Ed's CANFAR funding?}
